The limits of self commitment and private paternalism \thanks{}

### 2020-09-01 main.tex
table ss with pre-experiment data

\title{The limits of self-commitment and private paternalism \thanks{We want to thank Craig McIntosh and Mauricio Romero for advice and encouragement. We want to thank also Ricardo Olivares for excellent research assistance and Erick Molina's help with formatting. Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM provided valuable feedback.}}
\author{Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx;  
Seira: ITAM, enrique.seira@gmail.com} }
\date{This draft:  \today \\[2 cm]}

@@

Many institutions ---firms, schools, financial contracts--- restrict choice using built-in commitment mechanisms which help workers, students, borrowers overcome self-control problems. For instance, mortgages restrict choice ``with a fixed repayment stream and mandatory principal repayment \citep{Laibson2018}''.\footnote{\cite{Laibson2018} also mentions that ``Firms do limit their workers' freedom with intermediate deadlines, progress reports, production targets'', and schools with ``pop quizzes, classroom attendance requirements, cold calling, graded problem sets, deadlines''.} At the same time  these same firms shroud these forcing mechanisms and don't market their commitment features, presumably because students, workers and borrowers ``don't welcome these paternalistic restrictions'' (\cite{Laibson2018}). \cite{Laibson2018} argues that this presents an important commitment puzzle: if clients were present biased and sophisticated about their self control problem they should appreciate commitment features and firms should be eager to market them. That this is not so suggests some clients may be naive about their self control problems, and that private paternalism may be beneficial.\footnote{\cite{Laibson2018} defines paternalism as a policy that advances an individual's interests by restricting his or her freedom, and private paternalism as paternalism implemented by private institutions. In this paper we will study the effect of restricting freedom of choice on pawn recovery and financing cost, not overall welfare.}

This paper studies the benefits of restricting choice in the context of pawnbroker lending. Pawn loans are one of the oldest, understudied, and most prevalent forms of borrowing. There are more than 11,000 pawn shops across the US with 30 million clients and \$14 billion yearly revenues (in China is a 43 billion industry).\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.\footnote{For comparison there were 2.3 million micro-finance clients in Mexico in 2009 (\cite{Pedroza:2010}).} The key characteristic of pawn loans is that the borrower leaves personal property (a pawn) as collateral in exchange of an immediate cash loan of a smaller value. In our case Lender $P$ only accepts gold jewelry as collateral and approves all pawns, giving cash the equivalent of 70\% of the pawn's appraised value. The contract stipulates a 7\% monthly interest rate charged daily, a loan term of 90 days, and the flexibility to pay back the loan at anytime before the loan is due. In spite of this flexibility, most people lose their pawn, and among those that recover it almost all of them pay in the last days, just before the loan elapses.\footnote{In the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).}

@@

\begin{comment}
Lender $P$ offers a very simple but highly collateralized contract. It only accepts gold jewelry as collateral and approves all gold pawns, giving in cash the equivalent of 70\% of the weighted gold value. The contract stipulates a 7\% monthly interest rate charged daily, and a loan term of 90 days plus 15 grace days to pay the principal and the accumulated interest. The client has complete flexibility to pay any number of times any amount she desires towards the recovery of her pawn, with no pre-payment penalties. However if the total amount of principal plus interest is not covered by the end of the 105 days, she loses her pawn and all the payments that have been done (unless she renews the loan before this by paying all accumulated interest). All transactions ---appraisal of the piece, loan disbursement and loan servicing--- are conducted at the branch. The gold collateral is highly liquid and the pawnshop has an associated business that sells the gold jewelry. Given the over-collateralization of the loan one would expect no moral hazard or adverse selection on the part of borrowers. %This lets us focus more cleanly on behavioral economics aspects.
\end{comment}

We implemented a large randomized control trial with close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City. We answer five main questions using this experiment. First, would clients benefit  ---in terms of recovering their pawn and in terms of incurring in lower financing costs---  from having a frequent (monthly) payment commitment contract \textit{forced} on them, instead of the current 3-month pay-when-you-want contract? That is, we are asking whether \textit{charging} them a 2\% late payment fee for not paying a monthly installment on time can actually \textit{decrease} total (fee-inclusive) financing cost. Second, would there be demand for such a frequent payment commitment contract vis-a-vis the status quo one if given choice? Any payment profile implemented in the commitment contract can be replicated by the borrower under the status quo contract, but the later affords more flexibility to respond to income shocks without incurring in fees. Third, what types of clients would demand these contracts that restrict choice? Fourth, are late payment fees key to provide commitment or would a non-pecuniary but salient personal promise to pay provide a cost-reducing mix of commitment vs flexibility? Promises change behavior significantly in laboratory settings, but we know little about their effect in natural environments.\footnote{Some papers in this space are \cite{PromisesPartnerships}, \cite{Vanberg}, \cite{Belot2010}, \cite{WhyDoPromises}, \cite{FurtherPromises}, \cite{Ismayilov2017}. There is also some actual policy around using promises for loans: the government Mexico has created a program called ``Loans on your word'' for uncollateralized borrowing (\url{http://tiny.cc/yfmnmz}), but unfortunately there is little information about them.} Finally, is \textit{giving choice} among contracts better than forcing them into payment-commitment contracts in terms of minimizing financing costs incurred and the likelihood of recovering their pawn? Or on the contrary, is it better to force the commitment contract 
paternalistically?

@@

Forcing clients into frequent payment commitment contracts causes them on average to save on financing cost and to recover their pawn more. The effects are large: financing cost decreases by 9.5\% on average, from \$3161 to \$2857 MXN, while the likelihood of recovering their pawn increases by 25\%, from 43\% to 54\%. Results are robust to including transport costs of going to the branch plus losing a day's wage for each visit. Importantly, the benefits are distributed broadly: almost the whole distribution of treatment effects shows cost savings; however those most economically vulnerable, those that report being stressed, and those we classify as overconfident experience larger gains. %The commitment contract also causes payments to start 8 days earlier and be 16\% more frequent, compared to the control group. 
Treatment effects are concentrated on the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery. The fee-commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster and thus recover their pawn more at a cheaper financial cost. Finally, borrowers assigned to the forced fee-commitment contract are 5 percentage points (55\% of the mean) more likely than the control group to ask for another loan in the future, suggesting that they liked the commitment contract more after experiencing it.

@@

In spite of these estimated benefits for almost all clients, actual demand for the fee-commitment contract is low. Only 10\% of the group offered a choice between the monthly payment fee-commitment contract and the status-quo one chose the former. This is not likely driven by misunderstanding the (already simple) contract.\footnote{We posted two persons in each of the experiment's branches every day for all branch opening hours to carefully explain the contracts; material was developed to explain the differences among the two contracts, and subjects spelled back to our team the loan differences. Furthermore take up is systematically predicted by baseline covariates, making it less likely that it is just random mistakes.} Low demand for commitment is consistent with a large literature (\cite{Laibson2015}, \cite{Laibson2018}, \cite{John}, \cite{Ted}, \cite{Rabin2018}). 
%\footnote{\cite{Alcohol} and \cite{Kremer} are some of the few instances of high demand for commitment. \cite{Alcohol} speculates that this difference may be explained by their subjects having more experience with their self control problem. Close to ninety percent of our subjects claim to have pawned before. We find that experience does not predict positive take up in our sample.} 
%\cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can severely limit take-up when agents are naive about their self control, even though commitment could be welfare improving for them. 
Owing to this low take-up, we estimate zero average treatment effects of the \textit{fee-choice} arm on financial cost and on pawn recovery and throughout the quantile distribution.

@@

Combining the forcing and the choice arms ---a unique feature of our experiment--- allows us to estimate the counterfactuals to answer the following question how much money is left on the table by the prevalence of the status-quo choice? We calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost. On average they spend an extra \$238 MXN, close to 11\% of the average loan value. In particular 92\% of those that chose the status-quo contract would have been better in the fee-commitment contract, while only 8\% of those who chose the fee-commitment contract would have been better in the status-quo one. This suggests that forcing clients into commitment contacts (i.e. private paternalism) may be beneficial for the overwhelming majority of clients. After seeing our results Lender $P$ introduced frequent payment contracts in their loans portfolio.

We want to clarify that in the paper we are using the word ``paternalism'' in a restricted sense, meaning only that a large majority of clients would incur in lower financial costs from being forced into commitment contracts instead of letting them chose. We are not making claims about overall welfare which is a slippery concept once we accept the possibility of biased beliefs and preferences.

Inspired by a significant lab experiment literature on the effects of promises on behavior, and by research showing that a small fee could drastically reduce demand for commitment of naive present-biased borrowers (\cite{Laibson2015}), we implemented a ``psychological commitment'' in the form of a salient promise to pay.  \cite{PromisesPartnerships}, \cite{FurtherPromises}, \cite{Vanberg}, and \cite{Ismayilov2017} find that the ability to make a promise about behaving a certain way makes the individual more likely to adhere to the promised behavior. %and also induces trusting behavior by the recipients of the promise. 
To measure the causal effect of promises we implemented two other treatment arms. A \textit{promise-forcing} arm exactly analogous to our \textit{fee-forcing arm} except that instead of telling them that there is a fee if they don't pay on time, we made borrowers promise that they would pay one third of the amount in each of the 3 months, and told them that if they didn't they would have broken their promise and failed their word. Because salience is key we made them sign a (non-legally binding) personal promise and emphasized we were counting on them to keep their promise. A final arm (\textit{promise-choice arm}) gave clients the opportunity to choose between the \textit{Promise} contract and the \textit{Status-quo} contract.

We document two main results in the promise arms. First, demand for the commitment-promise contract is three times bigger than for the commitment fee contract, with 31\% take-up. This difference between both choice arms suggests that clients are indeed understanding and taking into account the contractual parameters in their choice, and that the fee commitment was probably too strong from their point of view. In spite of this much higher take-up, the \textit{Promise-choice arm} had no effect on outcomes on average, or even for those who selected into promising. Second, being forced in to the \textit{Promise} contract also had zero effects on average and throughout the distribution on financing cost and pawn recovery. %\footnote{There is a decrease in financial cost in the 50th and 75th quantiles in the forced promise-commitment arm however.}
Promises did not provide enough commitment so as to be reflected in behavior.

This paper contributes to several strands of literature. First, to the broad literature on commitment demand. A significant literature has shown that demand for commitment exists but is somewhat low in some contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}), and high in others (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}). We add to this literature by showing that very small fees are enough to drastically reduce demand for commitment, even when commitment is beneficial, and that softer commitments in the form of non-pecuniary personal promises elicit higher demand.\footnote{Our fees are 16 times smaller than than those of \cite{John} as a fraction of the loan/goal, and five times smaller converting peso values using exchange rates.} Second, \cite{Ted} and \cite{John} show the extent of commitment needed is underestimated even among those that buy it, and that subjects hurt themselves by self-imposing too weak a commitment in the intensive margin. We contribute in design by not allowing choice of the extent of commitment, and methodologically by inferring subjects underestimation of the value of commitment ex-ante from forgone treatment savings, instead of from subjects failing to reach their goal ex-post. Third, we focus on an important new context: pawnshop borrowing. Pawnshop borrowing is extremely prevalent in developing countries and very worrisome to regulators, yet severely understudied.\footnote{The World Bank's CGAP recognizes the importance of pawnshop borrowing worldwide but provides no statistics or analysis on it: \url{https://tinyurl.com/ydgob8pv}.}

Fourth, we study \textit{both} causal effects and selection into frequent payment commitment loan contracts. \cite{Ghatak} state that ``high-frequency repayment, a feature in nearly all microfinance contracts, has been largely overlooked''. %\footnote{\cite{LittleAtAtime} also note that ``it is especially surprising that there is so little analytical discussion of the incentive effects of the installment system''.} 
This paper fills part of this gap. Studying causal effects of installment payment frequency \cite{Pande} find null effects loan default, a surprising result given the prevalence of frequent payment contracts. In contrast  we find strong effects of payment frequency on decreased default.\footnote{There are many differences in context between the papers which may explain the different result. \cite{Pande} focus on group lending with very little default to start with (less than 1\%), while in our case almost half of loans end in default. We also have a larger sample and we focus on individualized loans, which may afford us stronger statistical power to detect effects.} Our result is consistent with \cite{Field} who show that delaying payment in microfinance loans increases default.\footnote{\cite{Craig} use the discipline of regular loan repayments in microfinance to remind people to save and make a savings plan, and find large increases in savings.} On the other hand, studying selection into frequent payment microfinance loans, \cite{Murdoch} conjecture that ``[frequent installment payment] structure is potentially beneficial in fostering discipline among present-biased borrowers'' and may explain why borrowers choose it.  They show that a robust positive correlation exists between displaying present biased preferences in surveys and selecting into microfinance, which they interpret as being due to high demand for the discipline imposed by frequent payments. However they acknowledge that this ``interpretation is suggestive... and needs to be confirmed by studies that establish causal links''. Our experimental \textit{is} a test of this causal link. We can isolate the pure effect of payment frequency on demand by randomly changing just this aspect of the contract. Our experimental results reject the hypothesis that microfinance (pawnshop) clients like and demand frequent payments, at least in our context. Importantly, our unique experimental design which simultaneously combines forcing and choice arms, paired with new machine learning methods to estimate heterogeneous treatment effects (\cite{atheygrf}), allows us to estimate whether there is positive or negative selection into beneficial contracts, and whether pawnshop clients forgo money by not demanding commitment. In consonance with what \cite{Walters} finds in another context, we find that it is not the case that those that benefit most from the contract demand it more. \cite{Sprenger} find a result that is similar to ours: that people how most need commitment (in our case the overconfident who show the greatest financial cost savings) are less likely to demand it. In contrast to \cite{Sprenger}, our context allows us to focus on money savings instead of estimated utility to proxy for benefits of commitment, a narrower but simpler measure. This allows us to measure effects on cost outcomes beyond take up and behavior. Our larger sample allow us to estimate heterogeneous treatment effects non-parametrically and perform counterfactuals this way. Finally, as in \cite{Rabin2018} we are able to contrasts subjects predictions of their behavior with their actual behavior, and how these map to outcomes, but we do it in a natural setting.

Fifth, we also contribute to the literature on the effect of promises by testing their effect on the field. In consonance to this literature we find that people are willing and indeed voluntarily choose to make promises. In contrast to lab evidence however measured behavior was unchanged by promising and people did not keep their promise.\footnote{This is of course not a refutation of this literature. %not least because the laboratory literature is implemented on more tightly controlled environments and focused on subtler aspects of promising, like their effects on second order beliefs and guilt aversion. The context is also different since 
The lab literature has focused mostly on very concrete investment games between two players and looked at the effects of promises on trust and cooperation in those games. However our results do provide a first piece of evidence on the limitations of using promises to change behavior in the field.}

@@

\section{Context and Data} \label{context}

@@

Pawn borrowing is one of the oldest forms of borrowing and one to which people with little access to the formal credit market turn to for ``emergency'' loans. They existed in antiquity at least since the Roman Empire, and there are records of it in China about 1,500 years ago (\cite{PawnShops}). As explained above pawn loans involve individuals leaving valuable and liquid assets (typically jewelry) as collateral in exchange for an immediate cash loan. We study such  context by partnering with Lender $P$, one of the largest pawn shops in Mexico, with more than one hundred branches spanning multiple States in Mexico.

%Lender $P$ was interested in understanding why half of their clients lost their pawn. Default is high in this context  compared to many papers in the microfinance literature.\footnote{\cite{Pande} study of the effect of payment frequency in a context where the rate of default is close to 1\%.} 
We study a context with high borrower default. 60\% of clients lose their pawn in a time span of 230 from the day of pawning. This default is likely inefficient since clients report a subjective value that is almost twice its gold value on average. It may also be detrimental from the lender's point of view since it may reduce the likelihood that the client becomes a return costumer, this may explain why Lender $P$ was interested in investigating whether a frequent payment contract would increase pawn recovery and costumer satisfaction, and whether there was demand for such a contract.

>>>>

\title{The limits of self-commitment and private paternalism \thanks{We want to thank Craig McIntosh, Mauricio Romero, and Anett John for advice and encouragement. Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting. Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM provided valuable feedback.}}
\author{Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Seira: ITAM, enrique.seira@gmail.com (corresponding author); Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx} }
\date{This draft:  \today \\[2 cm]}

@@

Many institutions ---firms, schools, financial contracts--- restrict choice using built-in commitment mechanisms which help workers, students, borrowers overcome self-control problems. For instance, ``[mortgages restrict choice] with a fixed repayment stream and mandatory principal repayment'' \citep{Laibson2018}.\footnote{\cite{Laibson2018} also mentions that ``Firms do limit their workers' freedom with intermediate deadlines, progress reports, production targets'', and schools with ``pop quizzes, classroom attendance requirements, cold calling, graded problem sets, deadlines''.} At the same time  these same firms shroud these forcing mechanisms and don't market their commitment features, presumably because students, workers and borrowers ``don't welcome these paternalistic restrictions''. \cite{Laibson2018} argues that this presents an important puzzle: clients that benefit from commitment although may underestimate its value and this have low demand for it. In such a case private paternalism may be beneficial.\footnote{\cite{Laibson2018} defines paternalism as a policy that advances an individual's interests by restricting his or her freedom, and private paternalism as paternalism implemented by private institutions. In this paper we will study the effect of restricting freedom of contract choice on two outcomes: pawn recovery and financing cost, not overall welfare.}

This paper studies the benefits of restricting choice in the context of pawnbroker lending. Pawn loans are one of the oldest, most understudied, and most prevalent forms of borrowing. There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a 43 billion dollar industry).\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.\footnote{For comparison there were 2.3 million micro-finance clients in Mexico in 2009 (\cite{Pedroza:2010}).} The key characteristic of pawn loans is that the borrower leaves personal property (a pawn) as collateral in exchange for an immediate cash loan of a smaller value. In our case Lender $P$ only accepts gold jewelry as collateral and approves all pawns, giving cash the equivalent of 70\% of the pawn's appraised value. The contract stipulates a 7\% monthly interest rate charged daily, a loan term of 90 days, and the flexibility to pay back the loan at anytime before the loan is due. In spite of this flexibility, most people lose their pawn, and among those that recover it almost all of them pay in the last days, just before the loan elapses.\footnote{In the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).}

@@

We implemented a large randomized control trial with close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City. We answer five main questions using this experiment. First, would clients benefit  ---in terms of recovering their pawn and in terms of incurring in lower financing costs---  from having a frequent (monthly) payment commitment contract \textit{forced} on them, instead of the current 3-month pay-when-you-want contract? That is, we are asking whether \textit{charging} them a 2\% late payment fee for not paying a monthly installment on time can actually \textit{decrease} total (fee-inclusive) financing cost. Second, would there be demand for such an installment contract vis-a-vis the status quo one if given choice? Any payment profile implemented in the commitment contract can be replicated by the borrower under the status quo contract, but the former provides commitment. Third, would clients who benefit from commitment the most (e.g. the present biased or overconfident) demand it more? Fourth, are late payment fees key to provide commitment or would a non-pecuniary but salient personal promise to pay provide a cost-reducing mix of commitment vs flexibility? Promises change behavior significantly in laboratory settings, but we know little about their effect in natural environments.\footnote{%Some papers in this space are \cite{PromisesPartnerships}, \cite{Vanberg}, \cite{Belot2010}, \cite{WhyDoPromises}, \cite{FurtherPromises}, \cite{Ismayilov2017}. 
There is some actual policy around using promises for loans: the government Mexico has created a program called ``Loans on your word'' for uncollateralized borrowing (\url{http://tiny.cc/yfmnmz}), but unfortunately there is little information about them.} Finally, is \textit{giving choice} among contracts better than forcing clients into payment-commitment contracts in terms of minimizing financing costs incurred and the likelihood of recovering their pawn? Or on the contrary, is it better to force the installment contract 
paternalistically?

@@

Forcing clients into frequent payment commitment contracts causes them on average to save on financing cost and to recover their pawn more. The effects are large: financing cost decreases by 9.5\% on average (from \$3161 to \$2857 MXN), while the likelihood of recovering their pawn increases by 25\% (from 43\% to 54\%). Results are robust qualitatively to including transport costs of going to the branch plus losing a day's wage for each visit. Importantly, the benefits are distributed broadly: almost the whole distribution of treatment effects shows cost savings; however those most economically vulnerable, and notably, those we classify as overconfident, experience larger gains. %The commitment contract also causes payments to start 8 days earlier and be 16\% more frequent, compared to the control group. 
Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery. The fee-commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster and thus recover their pawn more at a cheaper financial cost. Finally, borrowers assigned to the forced fee-commitment contract are 5 percentage points (55\% of the mean) more likely than the control group to ask for another loan in the future, suggesting that they liked the commitment contract after experiencing it.

@@

In spite of these estimated benefits for almost all clients, actual demand for the fee-commitment contract is low. Only 10\% of the group offered a choice between the monthly payment fee-commitment contract and the status-quo one chose the former. This is not likely driven by misunderstanding the (already simple) contract.\footnote{We posted two project assistants in each of the experimental branches every day for all branch opening hours to carefully explain the contracts; material was developed to explain the differences among the two contracts, and subjects spelled back to our team the loan differences. Furthermore take up is systematically predicted by baseline covariates, making it less likely that these are just random mistakes.} We show further that clients that most benefit from the contract (those who are overconfident about recovering) are \textit{less} likely to demand it, echoing a result by \cite{Sprenger}. %is Low demand for commitment is consistent with a large literature (\cite{Laibson2015}, \cite{Laibson2018}, \cite{John}, \cite{Ted}, \cite{Rabin2018}). 
%\footnote{\cite{Alcohol} and \cite{Kremer} are some of the few instances of high demand for commitment. \cite{Alcohol} speculates that this difference may be explained by their subjects having more experience with their self control problem. Close to ninety percent of our subjects claim to have pawned before. We find that experience does not predict positive take up in our sample.} 
%\cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can severely limit take-up when agents are naive about their self control, even though commitment could be welfare improving for them. 
Owing to this low take-up, we estimate zero average treatment effects of the \textit{fee-choice} arm on financial cost and on pawn recovery throughout the quantile distribution.

@@

Combining the forcing and the choice arms ---a unique feature of our experiment--- allows us to estimate the counterfactuals to answer the question of how much money is left on the table by giving choice to clients. We calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost. On average they spend an extra \$238 MXN, close to 11\% of the average loan value. In particular 92\% of those that chose the status-quo contract would have been better in the fee-commitment contract, while only 8\% of those who chose the fee-commitment contract would have been better in the status-quo one. This suggests that forcing clients into commitment contacts (i.e. private paternalism) may be beneficial for the overwhelming majority of clients. After seeing our results Lender $P$ introduced frequent payment contracts in their loans portfolio.

We want to clarify that in the paper we are using the word ``paternalism'' in a restricted sense, meaning only that a large majority of clients would incur in lower financial costs from being forced into installment contracts instead of letting them choose. We are not making claims about overall welfare which is a slippery concept if we take into account the possibility of biased beliefs and preferences.

Inspired by a significant lab experiment literature on the effects of promises on behavior, and by research showing that a small fee could drastically reduce demand for commitment of (partly) naive present-biased borrowers (\cite{Laibson2015}), we implemented a ``psychological commitment'' in the form of a salient promise to pay.  \cite{PromisesPartnerships}, \cite{FurtherPromises}, \cite{Vanberg}, and \cite{Ismayilov2017} find that the ability to make a promise about behaving a certain way makes the individual more likely to adhere to the promised behavior. %and also induces trusting behavior by the recipients of the promise. 
To measure the causal effect of promises we implemented two other treatment arms. A \textit{promise-forcing} arm exactly analogous to our \textit{fee-forcing arm} except that instead of telling them that there was a fee if they didn't pay on time, we made borrowers promise that they would pay one third of the amount in each of the 3 months, and told them that if they didn't they would have broken their promise and not kept their word. Because salience is key we made them sign a (legally non-binding) personal promise and emphasized that we were counting on them to keep their promise. A final arm (\textit{promise-choice arm}) gave clients the opportunity to choose between the \textit{Promise} contract and the \textit{Status-quo} contract.

We document two main results in the promise arms. First, demand for the commitment-promise contract is three times larger than for the commitment fee contract, with 31\% take-up. This difference between both choice arms suggests that clients are indeed understanding and taking into account the contractual parameters in their choice, and that the fee commitment was probably too strong from their point of view. In spite of this much higher take-up, the \textit{Promise-choice arm} had no effect on outcomes on average, or even for those who selected into promising. Second, being forced in to the \textit{Promise} contract also had zero effects on average and throughout the distribution on financing cost and pawn recovery. %\footnote{There is a decrease in financial cost in the 50th and 75th quantiles in the forced promise-commitment arm however.}
Promises did not provide enough commitment so as to be reflected in behavior.

This paper contributes to several strands of literature. First, we focus on an important new context: pawnshop borrowing. Pawnshop borrowing is extremely prevalent in developing countries and very worrisome to regulators, yet severely understudied.\footnote{The World Bank's CGAP recognizes the importance of pawnshop borrowing worldwide but provides no statistics or analysis on it (\url{https://tinyurl.com/ydgob8pv}). We could not find peer-reviewed papers about it either.} It is different from microfinance in that it deals with emergency loans, and not loans for productive investment. Because of this, it may draw on a more vulnerable (and potentially more unsophisticated) population. Moreover, the trade-off between loan rigidity and investment found for microfinance \citep{Field} may not be there for pawn borrowing.  Second, a significant literature has shown that demand for commitment exists but is somewhat low in some contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}), and high in others (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}). We add to this literature by showing --although we may not be the only ones-- that very small fees\footnote{For instance our fees are 16 times smaller than than those of \cite{John} as a fraction of the loan/goal, and 5 times smaller converting peso values using exchange rates.} are enough to drastically reduce demand for commitment, even when commitment is cost-reducing. We also show that softer commitments in the form of non-pecuniary personal promises elicit higher demand but do not affect behavior or financing costs.

Third, \cite{John} and \cite{Ted} show that the extent of commitment needed is underestimated even among those that purchase commitment mechanisms, and that subjects hurt themselves by self-imposing too weak a commitment in the intensive margin. We contribute in design by not allowing choice of the extent of commitment, and methodologically by inferring subjects underestimation of the value of commitment ex-ante from forgone treatment savings, instead of from subjects failing to reach a goal ex-post. In consonance with \cite{Sprenger} but in our very different context, we find that people who most need commitment (in our case the overconfident, as they have the larger treatment effects) are also the ones less likely to demand it when given choice. In contrast to \cite{Sprenger}, our context allows us to focus on money savings instead of estimated utility to proxy for benefits of commitment, a narrower but more transparent measure. This allows us to measure effects on cost outcomes beyond take up. As in \cite{Rabin2018} we are able to contrast subjects' \textit{own predictions} of their behavior with their actual behavior, and how these map to outcomes, but we do it in a natural setting.

Fourth, and most importantly, we study both causal effects and selection into frequent payment commitment loan contracts at the same time and for the same population in a single experiment. We know of no other experiment in the credit market which simultaneously combines forcing and choice arms. This feature, when paired with new machine learning methods to estimate heterogeneous treatment effects (\cite{atheygrf}), allows us to show whether there is positive or negative selection into beneficial contracts, and whether pawnshop clients forego money by not demanding commitment. In consonance with what \cite{Walters} finds in the school choice context, we find that it is \textit{not}  those who benefit most from the contract that demand it more.

Studying causal effects of installment payment frequency, \cite{Pande} find null effects on loan default, a surprising result given the prevalence of frequent payment contracts. In contrast we find strong effects of payment frequency on decreased default.\footnote{There are many differences in context between the papers which may explain the different result. \cite{Pande} focus on group lending with very little default to start with (less than 1\%), while in our case almost half of loans end in default. We also have a larger sample and we focus on individualized loans, which may afford us stronger statistical power to detect effects.} Our result is consistent with \cite{Field} who show that delaying payment in microfinance loans increases default.\footnote{\cite{Craig} use the discipline of regular loan repayments in microfinance to remind people to save and make a savings plan, and find large increases in savings.} On the other hand, studying selection into frequent payment microfinance loans, \cite{Murdoch} show that a robust positive correlation exists between displaying present biased preferences in surveys and selecting into microfinance, which they interpret as being due to high demand for the discipline imposed by frequent payments. However they acknowledge that this ``interpretation is suggestive... and needs to be confirmed by studies that establish causal links''. Our experiment is a test of this causal link, and it rejects the hypothesis that the majority of microfinance (pawnshop) clients demand frequent payments contracts, at least in our context.

%\cite{Ghatak} state that ``high-frequency repayment, a feature in nearly all microfinance contracts, has been largely overlooked''. %\footnote{\cite{LittleAtAtime} also note that ``it is especially surprising that there is so little analytical discussion of the incentive effects of the installment system''.} 
%This paper fills part of this gap.

Finally, even though personal promises feature prominently in microfinance guidelines\footnote{e.g. \url{https://grameenfoundation.org/documents/GrameenGuidelines.pdf}, p.36.} we know of no other study that has tried to isolate their effects on loan repayment.  In concordance with this literature we find that people are willing and indeed voluntarily choose to make promises. We find however that measured behavior was unchanged by promising.\footnote{This is of course not a refutation of this literature by any means. %not least because the laboratory literature is implemented on more tightly controlled environments and focused on subtler aspects of promising, like their effects on second order beliefs and guilt aversion. The context is also different since 
The lab literature has focused mostly on very structured investment games between two players and looked at the effects of promises on trust and cooperation through guilt aversion and cost of lying channels. In our case the bank is not a strategic player that responds to the promise or a person (although the teller is). However, our results do provide a first piece of evidence on the limitations of using promises to change behavior in loan contracts.}

@@

\section{Context} \label{context}

\subsection{Pawnshop borrowing}

Pawn borrowing is one of the oldest forms of borrowing and one to which people with little access to the formal credit market turn to for ``emergency'' loans. They existed in antiquity at least since the Roman Empire, and there are records of it in China about 1,500 years ago (\cite{PawnShops}). As explained above, pawn loans involve individuals leaving valuable and liquid assets (typically jewelry) as collateral in exchange for an immediate cash loan, which is typically used to pay for emergencies.

%Lender $P$ was interested in understanding why half of their clients lost their pawn. Default is high in this context  compared to many papers in the microfinance literature.\footnote{\cite{Pande} study of the effect of payment frequency in a context where the rate of default is close to 1\%.}

In spite of it high prevalence, pawnshop borrowing has not received much attention in the economics literature. The closest product studied is payday loans. In developing countries, however payday, lending is likely small compared to pawnshop lending; the latter is faster and requires less documentation, allowing access to informal sector workers who receive their salaries in cash . According to \cite{Payday} to get a payday loan: ``All that a prospective borrower typically needs is a home address; a valid checking account; a driver’s license and Social Security number; a couple of pay stubs to verify employment; wages and pay dates; and minimum earnings of at least \$1,000 a month''. Although the author meant this list as an instance of low requirements, they would render virtually all poor households in the developing countries ineligible.

Payday lending is controversial and regulators have concerns with the sophistication of borrowers using it. The US congress has actually banned the payday lending industry from serving active military personnel, and some states in the US have imposed zoning restrictions, interest caps, and restrictions on serial borrowing as consumer protection measures against payday lending \citep{Payday}. The main source of concern is whether consumers that use these loans suffer from behavioral and cognitive biases which imply sub-optimal choices, and there is some evidence for this.\footnote{\cite{Bertrand} write that ``Under the view that the people borrowing from payday lenders are making an informed, utility-maximizing choice given the constraints that they face, one  would not expect additional information disclosure about the payday product to  alter their borrowing behavior'', but to the contrary they find that simply disclosing how financing costs add up reduced demand by 11\%. %\cite{Meltzer} finds that payday loan access leads to increased difficulty paying mortgage, rent and utilities bills.
} Similar concerns apply to pawnshop borrowing.

@@

We study pawnshop borroing by partnering with Lender $P$, one of the largest pawn shops in Mexico, with more than one hundred branches spanning multiple States in Mexico.  Our context is one with high borrower default: 60\% of clients lose their pawn in a time span of 230 days from the date of pawning. This default is likely inefficient since clients report a subjective value that is almost twice its gold value on average. It can also be detrimental from the lender's point of view since it may reduce the likelihood that the client becomes a return costumer; this would explain why Lender $P$ was interested in investigating whether a frequent payment contract would increase pawn recovery and costumer satisfaction, and whether there was demand for such a contract.

One potential explanation for high default is that clients are really just selling their gold piece. This is unlikely for several reasons: (a) the reported subjective value of the pawn is larger than the loan size for 86\% of them, (b) among those that lose their pawn 58\% paid a positive amount towards its recovery and on average paid 34\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, (c) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}). %(d) there is a lot of engagement with the lender after pawning even for those who lost their pawn. On average clients that lost their pawn paid 34\% of the value of their loan, and close to 42\% of clients extended the loan for another cycle and made payments in the second cycle (see Figure \ref{proxy_naive} in Appendix).
